Structural Divergence Analysis

### 2016-07-27 MultipleReportAllBetasZscore.Rmd
cambios 27/07/2016

    m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
    exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )
    exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)

@@

    m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
    theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T )

@@

    fit = lm(exp.smooth.norm.MSDi ~ theo.smooth.norm.MSDi )
    MSDi.fit = fitted.values(fit)
    MSDi.R2 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit) ^ 2 
    MSDi.MSE = mean((MSDi.fit - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)
    exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]

>>>>

    m.exp.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.exp.smooth.norm.dr.squarei.csv", sep = "")))
    exp.smooth.norm.MSDi = colMeans(m.exp.smooth.norm.dr.squarei, na.rm = T )

    exp.smooth.norm.MSDi = scale(sqrt(exp.smooth.norm.MSDi))[, 1]

    exp.smooth.norm.MSDi = exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]                                                                    
    exp.smooth.norm.MSDi.sd = apply(m.exp.smooth.norm.dr.squarei, 2, sd, na.rm = T)

@@

@@

    m.theo.smooth.norm.dr.squarei = read.csv(file.path(out.dir, paste(analysis.fname.id, "_out_m.theo.smooth.norm.dr.squarei.csv", sep = "")))
    theo.smooth.norm.MSDi = colMeans(m.theo.smooth.norm.dr.squarei, na.rm = T )
    MSDi.fit = scale(sqrt(theo.smooth.norm.MSDi))[, 1]               
    MSDi.fit = MSDi.fit[1:length(exp.smooth.norm.MSDi)]

    MSDi.R2 = cor(exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)], MSDi.fit) ^ 2 
    MSDi.MSE = mean((MSDi.fit - exp.smooth.norm.MSDi[!is.na(exp.smooth.norm.MSDi)]) ^ 2)

### 2016-07-27 OUT/analysis-structure-CM.Rmd
cambios 27/07/2016

source("OUT/out_subset_CA/multiplot.R")
source("OUT/out_subset_CA/my-functions.R")
```

@@

```{r set_run_variables}
# Set options
family = "globins"
R0 = 10
enm = "ANM"

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CA", sep = "")
```

@@

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

@@

# dat.with.means and standard errors
d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})

##

z.RSD.exp = d$mean.z.RSD[d$dataset == "exp"]
z.RSD.strong = d$mean.z.RSD[d$dataset == "mut+sel"]
z.RSD.mut = d$mean.z.RSD[d$dataset == "mut"]

m.min.da.CM.ca = read.csv(file.path(data.dir, "min.da.CM.ca.csv", sep = ""))[, 2:4]

data.csv = data.frame(m.min.da.CM.ca[1:151, ], "mean.z.RSD.exp" = z.RSD.exp, "mean.z.RSD.strong" = z.RSD.strong, "mean.z.RSD.mut" = z.RSD.mut)

write.csv(data.csv, file.path(data.dir, "data.da.csv", sep = ""))

m.min.da.CM = m.min.da.CM.ca$min.da.CM[1:151]

data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.mut - z.RSD.strong, "m.min.da.CM" = m.min.da.CM)

r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.CM), 2)

ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.CM)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.CM")

r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.CM), 2)

ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.CM)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 0.5, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.CM")

##

m.min.da.ca = m.min.da.CM.ca$min.da.ca[1:151]

data.plot = data.frame("d.exp.mut" = z.RSD.mut - z.RSD.exp, "d.exp.strong" = z.RSD.strong - z.RSD.exp, "m.min.da.ca" = m.min.da.ca)

r = round(cor(data.plot$d.exp.mut, data.plot$m.min.da.ca), 2)

ggplot(data.plot, aes(y = d.exp.mut, x = m.min.da.ca)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.mut - mean.z.RSD.exp", x = "min.da.ca")

r = round(cor(data.plot$d.exp.strong, data.plot$m.min.da.ca), 2)

ggplot(data.plot, aes(y = d.exp.strong, x = m.min.da.ca)) +
  geom_point()+
  geom_smooth(method = "lm") +
  geom_label(aes(x = 5, y = 2, label = paste("R =", as.character(r)))) +
    labs(y = "mean.z.RSD.strong - mean.z.RSD.exp", x = "min.da.ca")

#d$dataset = factor(d$dataset, levels = c("exp", "mut", "strong"))
d$label = as.character(d$site)
active.sites = d$site[d$shell == 0]

>>>>

source("OUT/out_subset_CM/multiplot.R")
source("OUT/out_subset_CM/my-functions.R")
```

@@

```{r set_run_variables}
# Set options
family = "globins"
R0 = 7.5
enm = "ANM"

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CM", sep = "")
```

@@

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

@@

# dat.with.means and standard errors
d = ddply(dat,c("dataset","site","AA","shell"), function(x) {
                mean.z.RSD = mean(x$z.RSD, na.rm = T)
                ndata = sum(!is.na(x$z.RSD))
                se.z.RSD = sd(x$z.RSD, na.rm = T) / sqrt(ndata)
                data.frame(mean.z.RSD, ndata, se.z.RSD)
})
#d$dataset = factor(d$dataset, levels = c("exp", "mut", "strong"))
d$label = as.character(d$site)
active.sites = d$site[d$shell == 0]

### 2016-07-27 OUT/analysis-structure-smooth-CA.Rmd
cambios 27/07/2016

source("OUT/out_subset_CM/multiplot.R")
source("OUT/out_subset_CM/my-functions.R")
```

@@

```{r set_run_variables}
# Set options
family = "globins"
R0 = 7.5
enm = "ANM"

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CM", sep = "")
```

@@

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

>>>>

source("OUT/out_subset_CA/multiplot.R")
source("OUT/out_subset_CA/my-functions.R")
```

@@

```{r set_run_variables}
# Set options
family = "globins"
R0 = 10
enm = "ANM"

# significance factors
f95 = 1.96
f99 = 2.6
f999 = 3.3
data.dir = paste("out_subset_CA", sep = "")
```

@@

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.smooth.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.smooth.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_10_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.smooth.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_10_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

### 2016-07-27 OUT/analysis-structure.Rmd
cambios 27/07/2016

---
title: "Structural Divergence Analysis"
author: "María Laura Marcos, Julian Echave"
date: "25 de julio de 2016"
output: html_document
---

@@

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

>>>>

---
title: "Structural Divergence Analysis"
author: "María Laura Marcos, Julian Echave"
date: "25 de julio de 2016"
output: pdf_document
---

@@

dri2.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.smooth.norm.dr.squarei.csv", sep = ""))
Pn.exp.fname = file.path(data.dir, paste(family,"_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.Pn.csv", sep = ""))
energy.exp.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.exp.va.csv", sep = ""))

dri2.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.smooth.norm.dr.squarei.csv", sep = ""))
Pn.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.strong.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_strong.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))

dri2.mut.fname = file.path(data.dir,paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.smooth.norm.dr.squarei.csv", sep = ""))
Pn.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.Pn.csv", sep = ""))
energy.mut.fname = file.path(data.dir, paste(family, "_R0_7.5_beta_no.sel_K.analysis_Keff_out_m.theo.va.csv", sep = ""))
